Data getter for peekbank analysis

### 2024-08-28 1_get_data.qmd
update filenames
fix df name

```{r}
ages <- d_trial_rt |>
  group_by(administration_id) |>
  summarise(age = mean(age))

@@

```{r}
saveRDS(d_trial, here("cached_intermediates","1_d_trial"))
saveRDS(d_sub, here("cached_intermediates","1_d_sub"))
```

>>>>

```{r}
ages <- d_trial_rt_unfiltered |>
  group_by(administration_id) |>
  summarise(age = mean(age))

@@

```{r}
saveRDS(d_trial, here("cached_intermediates","1_d_trial.Rds"))
saveRDS(d_sub, here("cached_intermediates","1_d_sub.Rds"))
```
